---
title: "Example: Estimate volume of stormwater"
author: "Alessandra Vidal Meza"
format: html
editor: visual
execute:
  warning: false
  message: false
---

```{r}
library(tidyverse)
library(here)
```

We created a function `predict_runoff` under `storm_runoff.R` and added documentation using **Roxygen**. Remember, to add a Roxygen skeleton:

-   Click anywhere within the function

-   Go to 'Code' in the top menu and click 'Insert Roxygen Skeleton'

Now, let's source the `storm_runoff.R` script so we can use the `predict_runoff` function.

```{r}
source(here::here("src", "storm_runoff.R"))
```

Next, estimate the stormwater volume for a watershed of 182 acres, over a range of estimates for the impervious fraction (from 0.6 to 0.8, by increments of 0.01).

```{r}
# Create imprevious fraction vector 
impervious_vec <- seq(from = 0.6, to = 0.8, by = 0.01)

# Use predict_runoff() function
volume <- predict_runoff(I = impervious_vec, A = 182)
```

Let's bind into a dataframe the imprevious fraction vector and the volumes estimated by `predict_runoff()`.

```{r}
watershed_df <- data.frame(impervious_vec, volume)
```

Finally, create a plot for **watershed_df**. Save plot using **here** package.

```{r}
ggplot(data = watershed_df,
       aes(x = impervious_vec,
           y = volume)) +
  geom_line() +
  geom_point() +
  theme_light()

ggsave(here::here("figs", "watershed_volume_plot.png"),
       height = 5, width = 8)
```

### Citation

Function adapted from [NCDENR Stormwater BMP Manual](https://files.nc.gov/ncdeq/Water%20Quality/Surface%20Water%20Protection/SPU/SPU%20-%20BMP%20Manual%20Documents/BMPMan-Ch03-SWCalcs-20090616-DWQ-SPU.pdf). Instructions provided by Professor Allison Horst for the EDS 221: Scientific Programming Essentials course from the Master of Environmental Data Science program at the Bren School of Environmental Science & Management.
